---
title: "Statistical test"
output: html_document
---
```{r}
male <- measurement[measurement$Sex == "Male",]
female <- measurement[measurement$Sex == "Female",]
hist(male$MOW.to.ITS.Ratio)
hist(female$MOW.to.ITS.Ratio)
male_log10 <- log10(male$MOW.to.ITS.Ratio)
female_log10 <- log10(max(female$MOW.to.ITS.Ratio+1) - female$MOW.to.ITS.Ratio)
hist(male_log10)
hist(female_log10)
shapiro.test(female_log10)

qqPlot(female_log10)
```{r}
#levene test 
library(car)
leveneTest(Apis$MOW.to.ITS.Ratio, Apis$Sex)
leveneTest(Augo$MOW.to.ITS.Ratio, Augo$Sex)
leveneTest(Bombm$MOW.to.ITS.Ratio, Bombm$Sex)
leveneTest(Bombv$MOW.to.ITS.Ratio, Bombv$Sex)
leveneTest(lasio$MOW.to.ITS.Ratio, lasio$Sex)
```
```{r}
#two sample t-test

t.test(Apis_male_Ratio$MOW.to.ITS.Ratio, Apis_female_Ratio$MOW.to.ITS.Ratio, var.equal = TRUE)
t.test(Augo_male_Ratio$MOW.to.ITS.Ratio, Augo_female_Ratio$MOW.to.ITS.Ratio, var.equal = TRUE)
t.test(Agap_male_Ratio$MOW.to.ITS.Ratio, Agap_female_Ratio$MOW.to.ITS.Ratio, var.equal = TRUE)
t.test(Bombusm_male_Ratio$MOW.to.ITS.Ratio, Bombusm_female_Ratio$MOW.to.ITS.Ratio, var.equal = TRUE)
t.test(Bombusv_male_Ratio$MOW.to.ITS.Ratio, Bombusv_female_Ratio$MOW.to.ITS.Ratio, var.equal = TRUE)

t.test(Lasio_male_Ratio$MOW.to.ITS.Ratio, Lasio_female_Ratio$MOW.to.ITS.Ratio, var.equal = TRUE)

t.test(Xylo_male_Ratio$MOW.to.ITS.Ratio, Xylo_female_Ratio$MOW.to.ITS.Ratio, var.equal = TRUE)
```
#facet_wrap(~ sex) used to subset data in geom ()


# residuals
# testing normality using residuals
```{r}
fit <- lm(measurement~Sex, data = measurement)
res <- fit$residuals 

citation("ggplot2")
citation("car")
```

